---
title: "Introduction to Survival Analaysis in R"
output: html_notebook
---

First we will cover the log-rank test and how to make Kaplan-Meier plots for visualizing survival curves.
We will begin by using the Ovarian dataset in the survival package

```{r}
library(data.table)
library(survival)
library(ggplot2)
library(dplyr)
library(survminer)
library(MASS)
library(Hmisc)
library(ggpubr)
```

```{r}
data(ovarian)
```

Log-rank test 

The Cox Proportional-Hazards Model 
```{r}
args(coxph)
```

"In  the  simple  case  of  right-censored  data,  the  call  to Surv takes  the  form Surv(time, event), where time is either the event time or the censoring time, and
event is a dummy variable coded 1 if the event is observed or 0 if the observation is censored"

```{r}
Rossi <- fread("Rossi_Data_arrest.txt", header=T)
Rossi[1:5, 1:10]
```

Cox regression of time to rearrest on time constant covariates 

```{r}
mod.allison <- coxph(Surv(week, arrest) ~
+     fin + age + race + wexp + mar + paro + prio,
+     data=Rossi)
```

